$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-27 paper/e6ssm-tuning-paper.tex
Added updated U(1)_I plot, added missing second half of sentence in acknowledgements

\acknowledgements We would like to thank R. Nevzorov for many useful
discussions and comments and Florian Staub for very helpful responses
regarding the gauge kinetic mixing contributions in SARAH. DH would
also like to thank A. Ismail and T. Rizzo. PA would like to thank
J.H.~Park, A.~Voigt and D.~Stockinger for useful discussion regarding
the use of FlexibleSUSY in this project. This work was supported by
the University of Adelaide and by the ARC Centre of Excellence for
Particle Physics at the Terascale.

>>>>

\acknowledgements We would like to thank R.~Nevzorov for many useful
discussions and comments and F.~Staub for very helpful responses
regarding the gauge kinetic mixing contributions in SARAH. DH would
also like to thank A.~Ismail and T.~Rizzo for their helpful comments
regarding fine tuning in the MSSM. 
PA would like to thank J.H.~Park, A.~Voigt and D.~Stockinger for 
useful discussion regarding the use of FlexibleSUSY in this project. 
This work was supported by the University of Adelaide and by the ARC 
Centre of Excellence for Particle Physics at the Terascale.
